Constructing the transition graphs of interacting hysterons

### 2022-05-30 Paper_draft.tex
Reworked piece on garden-of-Eden states for base graphs to reflect added piece in candidate graphs section

It should be noted that, when constructing the base graphs from all possible combinations of transitions, the resulting graphs often contain states that cannot be reached from the all-zero state. We refer to these states as garden-of-Eden states (Fig. \ref{fig:basegraphs_avalanches}b). We generally choose to ignore garden-of-Eden states. As a result, the base graphs as counted in Equation \ref{eq:graph_count} can contain duplicates, so that the true number of graphs turns out lower than this number. For example, for $N=3$, Equation \ref{eq:graph_count} gives that the number of base graphs is $6\times16=96$. When ignoring garden-of-Eden states, we find that the number of graphs is only 27.\\

>>>>

The number of graphs given by Equation \label{eq:graph_count} takes into account exchange symmetry, but not garden-of-Eden states (Section \ref{ssec:candidate_graphs}), and thus gives a maximum on the number of base graphs. For example, for $N=3$, the number of base graphs provided by Equation \ref{eq:graph_count} is 96, while ignoring garden-of-Eden states reduces the number of base graphs to 35 (Fig. \ref{fig:basegraphs_n3}).
